Stat 400 Project

### 2021-12-13 Stat 400 proj.Rmd
Vaccine Status

```{r}
#create starting positions and state function
starting_vals <- function(num_subjects, I_0, x_dim, y_dim){

@@

@@

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  colnames(df)[3] <- 'subjects'
  colnames(df)[4] <- 'incubation'
  colnames(df)[5] <- 'recovery'

@@

#Function for getting updated coordinates
update_coords <- function(og_df, delta_df){
  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
  new_df <- data.frame(new_mx)
  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
  new_df[,3] <- og_df[,3]
  new_df[,4] <- og_df[,4]
  new_df[,5] <- og_df[,5]
  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')
  new_df
}

@@

      crucial_distance <- rexp(1, 1/mean_crit_dist)

      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      if(d <= crucial_distance){
        newly_infected <- c(newly_infected, j)
      }

@@

#simulation function
simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
  end_day <- list()
  num_cases <- rep(NA, days)
  num_cases <- c(I_0, num_cases)
  num_new_cases <- rep(NA, days)

@@

#Testing
df <- starting_vals(1000, 2, 1, 1)
len <- get_step_length(df, 1, 1)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coords <- coord_checker(df, newdf, 1, 1)
coords
new_status <- infection_status(coords, 8)
new_status

set.seed(400)
n=50
y <- simulator(n,100,10,10,2,1)
x <- 0:n

ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')

>>>>

```{r}
#create starting positions and state function
starting_vals <- function(num_subjects, I_0, x_dim, y_dim, prop_vac){

@@

  #Determining if a person is vaccinated
  vac_ppl <- sample(x = 1:num_subjects, size = round(prop_vac * num_subjects), replace = F)
  vac_vec <- rep(F , num_subjects)
  vac_vec[vac_ppl] <- T

@@

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time, vac_vec))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  colnames(df)[3] <- 'subjects'
  colnames(df)[4] <- 'incubation'
  colnames(df)[5] <- 'recovery'
  colnames(df)[6] <- 'vaccine'

@@

#Function for getting updated coordinates
update_coords <- function(og_df, delta_df){
  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
  new_df <- data.frame(new_mx)
  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
  new_df[,3] <- og_df[,3]
  new_df[,4] <- og_df[,4]
  new_df[,5] <- og_df[,5]
  new_df[,6] <- og_df[,6]
  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery', 'vaccine')
  new_df
}

@@

      crucial_distance <- rexp(1, 1/mean_crit_dist)
      vaccine_status <- current_suceptable[j, 'vaccine']
      if(vaccine_status == T) {
        vac_eff <- as.logical(rbinom(1,1,.8))
      }
      else {
        vac_eff <- F
      }

      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      if(d <= crucial_distance & vac_eff == F){
        newly_infected <- c(newly_infected, j)
      }

@@

#simulation function
simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac){
  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0, prop_vac = prop_vac)
  end_day <- list()
  num_cases <- rep(NA, days)
  num_cases <- c(I_0, num_cases)
  num_new_cases <- rep(NA, days)

@@

#Testing
df <- starting_vals(1000, 2, 1, 1, .8)
len <- get_step_length(df, 1, 1)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coords <- coord_checker(df, newdf, 1, 1)
coords
new_status <- infection_status(coords, 8)
new_status

set.seed(400)
n=50
y <- simulator(n,100,10,10,2,1,.95)
x <- 0:n

plot <- ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')
